% !TeX root=./main.tex

\section{Conclusions}

I motivate a five-factor model of market, size, value, momentum and profitability factors,
B16, with buying cheap, profitable stocks. The intuition of pricing all assets means we
should focus on the interaction between factors. Value and momentum interact strongly. At
the same time, they have little interaction with profitability. Value, momentum and
profitability drive the maximum Sharpe ratio of 0.56. Statistically, value and momentum
are negatively correlated with each other but positively correlated with other portfolios
leading to slope enhancement in regressions. The economics behind their relationship may
be to do with identifying those stocks that will exhibit changes in book equity in the
future. Value and momentum make investment redundant as a factor because it does not add
anything to the maximum Sharpe ratio of the other five factors. Investment's lack of
contribution is driven by explained average return rather than unexplained variation in
returns through time.

In anomaly sorts, the GRS statistic does not provide as strong evidence in favour of the
B16 model as the maximum Sharpe ratio, although they agree B16 is the best model. Given
our desire to price all assets and the sensitivity of the GRS to the choice of test
assets, it is satisfactory that evidence was not as strong but still supportive of the B16
model. Individual regression slopes show that when controlling for value, the value factor
is not able to vary across investment portfolios and therefore the model does not perform
as well in these sorts. Portfolios where value and momentum pull in opposite directions
are a problem because these sorts negate the interaction between value and momentum. These
problem sorts share the “lethal combination” of returns - small, unprofitable stocks that
somehow invest aggressively.

Omissions include taking a stance on risk vs. behavioural stories, factor timing and
volatility managed portfolios. We can only say factors describe returns rather than
explain them if we do not take a stance on risk vs. behavioural stories for factors.
Arguments are largely statistical without putting forward the drivers behind factor
returns. I suggest future changes in book equity drive the interaction of value and
momentum subsuming investment, but this does not clear up why value and momentum generate
returns in the first place. Using many factors can be motivated by diversification to
protect against prolonged poor runs for individual factors. In this case an investor gives
up some of the upside of a factor to hedge another. From an investment perspective, it is
preferable to “time” factors as we might time the market instead of relying on
diversifying across factors. Dropping factors will lower the maximum Sharpe ratio of the
model. Furthermore, timing factors somewhat misses the point in an asset-pricing context.
Assets will have different exposures to different factors and to drop factors removes the
ability to capture those exposures. Volatility is the biggest asset-pricing anomaly. We
can use volatility when we weight stocks instead of relying on market equity. This
approach avoids the problem and does not explain the drivers behind the returns to
volatility.

The maximum Sharpe ratio provides a clear winner, B16. Test asset evidence leaves the
puzzle of why the model does not outperform other models to the extent the superior Sharpe
ratio suggests it should.
