% !TeX root=../main.tex

\subsection{Sharpe Ratio}

\import{./Tables/}{Table1}

Table \ref{tbl:Table1} panel A shows summary statistics for individual factors as well as the 
BS2015 and FF2016b models.
The market has a high average monthly return, 0.51\%, offset by a high standard deviation, 
4.42, giving a modest Sharpe ratio of 0.12.
Size, value and investment factors had similar average monthly returns and standard deviations 
giving Sharpe ratios from 0.09 to 0.15.
Momentum had the highest average monthly return at 0.66\%.
This does not translate to a significantly higher Sharpe ratio, 0.16, as the standard 
deviation is also high at 4.23.
Cash profitability has the highest Sharpe ratio of the individual factors at 0.27.
This is driven by the low standard deviation of 1.4 rather than a high average return, which 
is modest at 0.37\%.
The models do not improve the average monthly return, 0.42\% for BS2015 and 0.37\% for 
FF2016b, but do lower the standard deviation of returns to 0.69 and 0.75.
This results in significantly improved Sharpe ratios of 0.6 and 0.5.
Given the unimpressive monthly returns, we should keep in mind that models most 
appropriate for pricing may not be the most appropriate for investing 
\parencite{pastor2000comparing}.
We are concerned with the way our models co-vary with all assets, not whether they 
generate superior returns.

Table \ref{tbl:Table1} panel B shows the intercepts, standard deviation of the residuals, 
contribution to the maximum squared Sharpe ratio and the weight in the models for each factor.
For BS2015, value and profit factors contribute similar amounts, 0.22 and 0.2, to the Sharpe 
ratio.
This is in-line with our intuition that fairly-priced, profitable stocks will generate higher 
returns those relatively more expensive or less profitable.
Value's large contribution is driven primarily by a large intercept, 1.11, while 
profitability's contribution is driven by a low standard deviation of residuals, 1.16.
The market and momentum also have large intercepts, 1.32 and  1.11, but the higher standard 
deviation of residuals, 3.79 and 3.11, inhibit the factors' contributions to the BS2015 model, 
0.11 and 0.13.
Size contributes very little to the Sharpe ratio, 0.04.
Despite value and profitability's similar contributions to the Sharpe ratio of the BS2015 
model, the profit factor has a much higher weight than value, 0.45 compared to 0.23, in the 
portfolio which generates the maximum Sharpe ratio.
Other factor weights are in-line with contributions to Sharpe ratio.
For FF2016b, the market intercept is 1.09 but the high standard deviation of residuals, 3.76, 
drives a low contribution of 0.08.
Despite investment's low standard deviation of residuals, 1.38, its low intercept, 0.14, 
drives a negligible contribution of 0.01.
Size and value contribute similar amounts, 0.03 and 0.04, thanks to modest intercepts, 0.47 
and 0.36, coupled with modest standard deviations of residuals of 2.83 and 1.9.
Profitability contributes the most at 0.19 driven by a low standard deviation of residuals at 
1.19.
The profitability factor has the largest weight, 0.54, in the portfolio which maximizes the 
Sharpe ratio of FF2016b.
Remaining factors are all weighted between 0.09 and 0.15.

Factor contributions given the other four factors need not sum to the total model squared 
Sharpe ratio because $(a/\sigma)^2$ is the amount the squared Sharpe ratio of the four other 
factors is improved when the fifth is included.
A factor's contribution depends on the amount of its mean return, $a$, and variation, 
$\sigma$, that is left unexplained by the other factors.
Unexplained mean return is the traditional alpha from a time series regression while the 
unexplained variation is the standard deviation of the residuals from the same regression.
The unexplained mean return represents the potential to add information to the other factors 
in a model while the unexplained variation dampens the effect of unexplained factor return on 
the model's Sharpe ratio \parencite{fama2016choosing}.
