---
title: "Test Factors"
author: "Sam Thorold"
output:
  html_document:
    keep_md: true
    df_print: paged
    code_folding: show
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE, fig.height=4)
```

# Definitions and Links

- **[Variables](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/variable_definitions.html)**
- **[Factors](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/f-f_5_factors_2x3.html)**


- [Size breakpoints](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_me_breakpoints.html)
- [Size returns](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_port_form_sz.html)


- [Book-to-Market breakpoints](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_beme_breakpoints.html)
- [Book-to-Market returns](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_form_btm.html)


- [Operating Profit breakpoints](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_op_breakpoints.html)
- [Operating Profit returns](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_port_form_op.html)


- [Investment breakpoints](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_inv_breakpoints.html)
- [Investment returns](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_port_form_inv.html)


- [Momentum breakpoints](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_2-12_breakpoints.html)
- [Momentum returns](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_10_port_form_pr_12_2.html)

```{r libraries, message=FALSE, warning=FALSE}
library(data.table)
library(dplyr)
library(dtplyr)
library(ggplot2)
library(knitr)
library(rlang)
library(Rsolnp)
```

```{r define.stats.helpers}
se = function(x) sd(x, na.rm=TRUE)/sqrt(length(x))

t.stat = function(x) t.test(x)$statistic

sr = function(x) mean(x, na.rm=TRUE) / sd(x, na.rm=TRUE)
```

# My Factors

```{r}
f = fread("C:/Data/Thesis/factors.csv")

f = f[1:630,] %>% select(Rm, SMB, HML, HMLm, RMWo, RMWg, CMA, WML)

rbind(sapply(f, mean), sapply(f, se), sapply(f, t.stat), sapply(f, sr))  %>% round(2)
```

# French Dartmouth Web Factors

```{r}
ff = fread("C:/Data/FrenchDartmouth/FF_factors.csv")

ff = ff[1:630,] %>% select(-c(Date))
setnames(ff,
         c("Mkt-RF", "SMB", "HML", "RMW", "CMA"),
         c("FF.Rm", "FF.SMB", "FF.HML", "FF.RMW", "FF.CMA"))

rbind(sapply(ff, mean), sapply(ff, se), sapply(ff, t.stat))  %>% round(2)
```

```{r}
f = cbind(f, ff)
```

# Factor Correlation

```{r}
cor(f[1:630,]) %>% round(2)
```

# Maximum Sharpe Ratio

$$
E(R_p) = w^T R
$$

```{r}
ER = function(w, R) t(w)%*%R
```

$$
Var(R_p) = w^T \Omega w
$$

```{r}
VAR = function(w, covar.mat) t(w)%*%covar.mat%*%w
SD = function(w, covar.mat) sqrt(VAR(w, covar.mat))
```

```{r}
SR = function(w, factor.mat, covar.mat){

    w = matrix(w, nrow=length(w), ncol=1)

    R = matrix(colMeans(factor.mat), nrow=length(w), ncol=1)
    # -ve sign because we want to maximize and most optimizers minimize
    Rp = -ER(w, R)

    stdev = SD(w, covar.mat)

    return(Rp/stdev)
}
```

```{r}
SR.sq.mat = function(R, covar.mat) t(R)%*%solve(covar.mat)%*%R
```

```{r}
w.star.mat = function(Rp, R, covar.mat){
    return(((Rp/(SR.sq.mat(R, covar.mat)))[1])*solve(covar.mat)%*%R)
}
```

```{r}
# The objective function and the constraint function have to take the same
# arguments
sum.constraint = function(w, factor.mat, covar.mat){
    return(sum(w))
}
```

## Rm, SMB, HML

```{r}
factor.mat = f %>% select(FF.Rm, FF.SMB, FF.HML)

R = matrix(colMeans(factor.mat), nrow=ncol(factor.mat), ncol=1)
covar.mat = cov(factor.mat)

rbind(SR.sq.mat(R, covar.mat), sqrt(SR.sq.mat(R, covar.mat))) %>% round(4)
```

## Rm, SMB, HML, RMW, CMA

```{r}
factor.mat = f %>% select(FF.Rm, FF.SMB, FF.HML, FF.RMW, FF.CMA)
factor.mat = factor.mat[1:630,]

R = matrix(colMeans(factor.mat), nrow=ncol(factor.mat), ncol=1)
covar.mat = cov(factor.mat)

w0 = matrix(1/length(factor.mat), nrow=length(factor.mat))

rbind(SR.sq.mat(R, covar.mat), sqrt(SR.sq.mat(R, covar.mat)[1])) %>% round(4)

results = solnp(
    pars=w0, fun=SR, factor.mat=factor.mat, covar.mat=covar.mat,
    eqfun=sum.constraint, eqB=1, control=list(trace=0))

(-results$values^2) %>% round(4)
results$pars %>% round(4)
sum(results$par)

ER(results$pars, R) %>% round(2)
ER(c(.1, .09, .09, .43, .29), R) %>% round(2)
```

## Rm, SMB, RMW, CMA

```{r}
factor.mat = f %>% select(FF.Rm, FF.SMB, FF.RMW, FF.CMA)

R = matrix(colMeans(factor.mat), nrow=ncol(factor.mat), ncol=1)
covar.mat = cov(factor.mat)

sqrt(SR.sq.mat(R, covar.mat)) %>% round(4)
```

## Rm, SMB, RMW, CMA, WML

```{r}
factor.mat = f %>% select(FF.Rm, FF.SMB, FF.RMW, FF.CMA, WML)

R = matrix(colMeans(factor.mat), nrow=ncol(factor.mat), ncol=1)
covar.mat = cov(factor.mat)

sqrt(SR.sq.mat(R, covar.mat)) %>% round(4)
```

## Rm, SMB, HML, RMW, CMA, WML

```{r}
factor.mat = f %>% select(FF.Rm, FF.SMB, FF.HML, FF.RMW, FF.CMA, WML)

R = matrix(colMeans(factor.mat), nrow=ncol(factor.mat), ncol=1)
covar.mat = cov(factor.mat)

sqrt(SR.sq.mat(R, covar.mat)) %>% round(4)
```

## Rm, SMB, HML_M, RMW, CMA, WML

```{r}
factor.mat = f %>% select(FF.Rm, FF.SMB, HMLm, FF.RMW, FF.CMA, WML)

R = matrix(colMeans(factor.mat), nrow=ncol(factor.mat), ncol=1)
covar.mat = cov(factor.mat)

sqrt(SR.sq.mat(R, covar.mat)) %>% round(4)
```

## Rm, SMB, HML_M, RMW_g, CMA, WML

```{r}
factor.mat = f %>% select(FF.Rm, FF.SMB, HMLm, RMWg, FF.CMA, WML)

R = matrix(colMeans(factor.mat), nrow=ncol(factor.mat), ncol=1)
covar.mat = cov(factor.mat)

sqrt(SR.sq.mat(R, covar.mat)) %>% round(4)
```

## Rm, SMB, HML_M, RMW_g, WML

```{r}
factor.mat = f %>% select(FF.Rm, FF.SMB, HMLm, RMWg, WML)

R = matrix(colMeans(factor.mat), nrow=ncol(factor.mat), ncol=1)
covar.mat = cov(factor.mat)

sqrt(SR.sq.mat(R, covar.mat)) %>% round(4)
```

```{r}
#w0 = c(1/3, 1/3, 1/3)
#results = solnp(
#    w0, SR, factor.mat=factor.mat, covar.mat=covar.mat,
#    eqfun=sum.constraint, eqB=c(1), control=list(trace=0))
#results$pars %>% round(4)
#sum(results$par)
#-results$values %>% round(4)
```

```{r}
#factor.mat = f %>% select(RF, FF.Rm, FF.SMB, FF.HML)

#R = matrix(colMeans(factor.mat), nrow=ncol(factor.mat), ncol=1)
#covar.mat = cov(factor.mat)

w0 = c(1/5, 1/5, 1/5, 1/5, 1/5)
#SR(w0, factor.mat, covar.mat)

SR.sq.mat(R, covar.mat) %>% round(4)

results = solnp(
    pars=w0, SR, factor.mat=factor.mat, covar.mat=covar.mat,
    eqfun=sum.constraint, eqB=1, control=list(trace=0))
results$pars %>% round(4)
sum(results$par)
-results$values %>% round(4)

w.star = results$pars
ER(w.star, R)
w.star.mat(ER(w.star, R), R, covar.mat) %>% round(4)
```

