---
title: "Test Factors"
author: "Sam Thorold"
output:
  html_document:
    keep_md: true
    df_print: paged
    code_folding: show
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE, fig.height=4)
```

# Definitions and Links

- **[Variables](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/variable_definitions.html)**
- **[Factors](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/f-f_5_factors_2x3.html)**


- [Size breakpoints](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_me_breakpoints.html)
- [Size returns](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_port_form_sz.html)


- [Book-to-Market breakpoints](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_beme_breakpoints.html)
- [Book-to-Market returns](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_form_btm.html)


- [Operating Profit breakpoints](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_op_breakpoints.html)
- [Operating Profit returns](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_port_form_op.html)


- [Investment breakpoints](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_inv_breakpoints.html)
- [Investment returns](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_port_form_inv.html)


- [Momentum breakpoints](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_2-12_breakpoints.html)
- [Momentum returns](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/Data_Library/det_10_port_form_pr_12_2.html)

```{r libraries, message=FALSE, warning=FALSE}
library(data.table)
library(dplyr)
library(dtplyr)
library(ggplot2)
library(knitr)
library(rlang)
library(Rsolnp)
```

```{r define.stats.helpers}
se = function(x) sd(x, na.rm=TRUE)/sqrt(length(x))

t.stat = function(x) t.test(x)$statistic

sr = function(x) mean(x, na.rm=TRUE) / sd(x, na.rm=TRUE)

stat.summary = function(df){
    return(
        rbind(sapply(df, mean), sapply(df, se), sapply(df, t.stat), sapply(df, sr))
    )
}
```

# My Factors

```{r}
f = fread("C:/Data/Thesis/factors.csv")

colnames(f)

f = f[1:630,]  %>% select(
    -c(V1, Date, SMB.HML, SMB.HMLm, SMB.RMWo, SMB.RMWor, SMB.RMWg, SMB.RMWc, SMB.CMA, SMB.WML)
)

rbind(sapply(f, mean), sapply(f, se), sapply(f, t.stat), sapply(f, sr))  %>% round(2)
```

# French Dartmouth Web Factors

```{r}
ff = fread("C:/Data/FrenchDartmouth/FF_factors.csv")

ff = ff[1:630,] %>% select(-c(Date))
setnames(ff,
         c("Mkt-RF", "SMB", "HML", "RMW", "CMA"),
         c("FF.Rm", "FF.SMB", "FF.HML", "FF.RMW", "FF.CMA"))

rbind(sapply(ff, mean), sapply(ff, se), sapply(ff, t.stat))  %>% round(2)
```

```{r}
f = cbind(f, ff)
```

# Factor Correlation

```{r}
cor(f[1:630,]) %>% round(2)
```

# Maximum Sharpe Ratio

$$
E(R_p) = w^T R
$$

```{r}
ER = function(w, R) t(w)%*%R
```

$$
Var(R_p) = w^T \Omega w
$$

```{r}
VAR = function(w, covar.mat) t(w)%*%covar.mat%*%w
SD = function(w, covar.mat) sqrt(VAR(w, covar.mat))
```

```{r}
# Objective function passed to one of R's minimizing thingies
SR.obj = function(w, factor.mat, covar.mat){

    w = matrix(w, nrow=length(w), ncol=1)

    R = matrix(colMeans(factor.mat), nrow=length(w), ncol=1)
    # -ve sign because we want to maximize and most optimizers minimize
    Rp = -ER(w, R)

    stdev = SD(w, covar.mat)

    return(Rp/stdev)
}
```

```{r}
SR.sq.mat = function(R, covar.mat) t(R)%*%solve(covar.mat)%*%R
```

```{r}
w.star.mat = function(Rp, R, covar.mat){
    return(((Rp/(SR.sq.mat(R, covar.mat)))[1])*solve(covar.mat)%*%R)
}
```

```{r}
# The objective function and the constraint function have to take the same
# arguments
sum.constraint = function(w, factor.mat, covar.mat){
    return(sum(w))
}
```

# Fama and French (2016) Table 3

## Rm, SMB, HML, RMWor, CMA

```{r}
factor.mat = f %>% select(FF.Rm, FF.SMB, FF.HML, RMWor, FF.CMA)
factor.mat = factor.mat[1:630,]  # through 2015-12

R = matrix(colMeans(factor.mat), nrow=ncol(factor.mat), ncol=1)
covar.mat = cov(factor.mat)

# Max Sharpe Ratio
Sh2 = rbind(SR.sq.mat(R, covar.mat), sqrt(SR.sq.mat(R, covar.mat)[1]))[1]

# Marginal contributions from spanning regression

fit = lm(FF.Rm ~ FF.SMB + FF.HML + RMWor + FF.CMA, data=factor.mat)
# round(coef(fit), 3)
# round(sd(fit$residuals), 3)
Mkt = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.SMB ~ FF.Rm + FF.HML + RMWor + FF.CMA, data=factor.mat)
# round(coef(fit), 3)
# round(sd(fit$residuals), 3)
Size = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.HML ~ FF.Rm + FF.SMB + RMWor + FF.CMA, data=factor.mat)
# round(coef(fit), 3)
# round(sd(fit$residuals), 3)
Val = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(RMWor ~ FF.Rm + FF.SMB + FF.HML + FF.CMA, data=factor.mat)
# round(coef(fit), 3)
# round(sd(fit$residuals), 3)
Prof = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.CMA ~ FF.Rm + FF.SMB + FF.HML + RMWor, data=factor.mat)
# round(coef(fit), 3)
# round(sd(fit$residuals), 3)
Inv = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

RMWor = cbind(Sh2, Mkt, Size, Val, Prof, Inv)
rownames(RMWor) = c("Mkt, SMB, HML, RMWor, CMA")
# round(RMWor, 3)
```

## Rm, SMB, HML, RMWc, CMA

```{r}
factor.mat = f %>% select(FF.Rm, FF.SMB, FF.HML, RMWc, FF.CMA)
factor.mat = factor.mat[1:630,]  # through 2015-12

R = matrix(colMeans(factor.mat), nrow=ncol(factor.mat), ncol=1)
covar.mat = cov(factor.mat)

# Max Sharpe Ratio
Sh2 = rbind(SR.sq.mat(R, covar.mat), sqrt(SR.sq.mat(R, covar.mat)[1]))[1]

# Marginal contributions from spanning regression

fit = lm(FF.Rm ~ FF.SMB + FF.HML + RMWc + FF.CMA, data=factor.mat)
Mkt = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.SMB ~ FF.Rm + FF.HML + RMWc + FF.CMA, data=factor.mat)
Size = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.HML ~ FF.Rm + FF.SMB + RMWc + FF.CMA, data=factor.mat)
Val = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(RMWc ~ FF.Rm + FF.SMB + FF.HML + FF.CMA, data=factor.mat)
Prof = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.CMA ~ FF.Rm + FF.SMB + FF.HML + RMWc, data=factor.mat)
Inv = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

RMWc = cbind(Sh2, Mkt, Size, Val, Prof, Inv)
rownames(RMWc) = c("Mkt, SMB, HML, RMWc, CMA")
res = rbind(RMWor, RMWc)
# round(res, 3)
```

## Rm, SMB, HML, RMWg, CMA

```{r}
factor.mat = f %>% select(FF.Rm, FF.SMB, FF.HML, RMWg, FF.CMA)
factor.mat = factor.mat[1:630,]  # through 2015-12

R = matrix(colMeans(factor.mat), nrow=ncol(factor.mat), ncol=1)
covar.mat = cov(factor.mat)

# Max Sharpe Ratio
Sh2 = rbind(SR.sq.mat(R, covar.mat), sqrt(SR.sq.mat(R, covar.mat)[1]))[1]

# Marginal contributions from spanning regression

fit = lm(FF.Rm ~ FF.SMB + FF.HML + RMWg + FF.CMA, data=factor.mat)
Mkt = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.SMB ~ FF.Rm + FF.HML + RMWg + FF.CMA, data=factor.mat)
Size = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.HML ~ FF.Rm + FF.SMB + RMWg + FF.CMA, data=factor.mat)
Val = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(RMWg ~ FF.Rm + FF.SMB + FF.HML + FF.CMA, data=factor.mat)
Prof = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.CMA ~ FF.Rm + FF.SMB + FF.HML + RMWg, data=factor.mat)
Inv = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

RMWg = cbind(Sh2, Mkt, Size, Val, Prof, Inv)
rownames(RMWg) = c("Mkt, SMB, HML, RMWg, CMA")
res = rbind(RMWor, RMWc, RMWg)
# round(res, 3)
```

## Rm, SMB, HML, RMWor, CMA, WML

```{r}
factor.mat = f %>% select(FF.Rm, FF.SMB, FF.HML, RMWor, FF.CMA, WML)
factor.mat = factor.mat[1:630,]  # through 2015-12

R = matrix(colMeans(factor.mat), nrow=ncol(factor.mat), ncol=1)
covar.mat = cov(factor.mat)

# Max Sharpe Ratio
Sh2 = rbind(SR.sq.mat(R, covar.mat), sqrt(SR.sq.mat(R, covar.mat)[1]))[1]

# Marginal contributions from spanning regression

fit = lm(FF.Rm ~ FF.SMB + FF.HML + RMWor + FF.CMA + WML, data=factor.mat)
# round(coef(fit), 3)
# round(sd(fit$residuals), 3)
Mkt = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.SMB ~ FF.Rm + FF.HML + RMWor + FF.CMA + WML, data=factor.mat)
# round(coef(fit), 3)
# round(sd(fit$residuals), 3)
Size = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.HML ~ FF.Rm + FF.SMB + RMWor + FF.CMA + WML, data=factor.mat)
# round(coef(fit), 3)
# round(sd(fit$residuals), 3)
Val = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(RMWor ~ FF.Rm + FF.SMB + FF.HML + FF.CMA + WML, data=factor.mat)
# round(coef(fit), 3)
# round(sd(fit$residuals), 3)
Prof = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.CMA ~ FF.Rm + FF.SMB + FF.HML + RMWor + WML, data=factor.mat)
# round(coef(fit), 3)
# round(sd(fit$residuals), 3)
Inv = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(WML ~ FF.Rm + FF.SMB + FF.HML + RMWor + FF.CMA, data=factor.mat)
# round(coef(fit), 3)
# round(sd(fit$residuals), 3)
Mom = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

RMWor = cbind(Sh2, Mkt, Size, Val, Prof, Inv, Mom)
rownames(RMWor) = c("Mkt, SMB, HML, RMWor, CMA, WML")
res = rbind(cbind(res, NA), RMWor)
colnames(res) = c("Sh2", "Mkt", "Size", "Val", "Prof", "Inv", "Mom")
# round(res, 3)
```

## Rm, SMB, HML, RMWc, CMA, WML

```{r}
factor.mat = f %>% select(FF.Rm, FF.SMB, FF.HML, RMWc, FF.CMA, WML)
factor.mat = factor.mat[1:630,]  # through 2015-12

R = matrix(colMeans(factor.mat), nrow=ncol(factor.mat), ncol=1)
covar.mat = cov(factor.mat)

# Max Sharpe Ratio
Sh2 = rbind(SR.sq.mat(R, covar.mat), sqrt(SR.sq.mat(R, covar.mat)[1]))[1]

# Marginal contributions from spanning regression

fit = lm(FF.Rm ~ FF.SMB + FF.HML + RMWc + FF.CMA + WML, data=factor.mat)
Mkt = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.SMB ~ FF.Rm + FF.HML + RMWc + FF.CMA + WML, data=factor.mat)
Size = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.HML ~ FF.Rm + FF.SMB + RMWc + FF.CMA + WML, data=factor.mat)
Val = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(RMWc ~ FF.Rm + FF.SMB + FF.HML + FF.CMA + WML, data=factor.mat)
Prof = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.CMA ~ FF.Rm + FF.SMB + FF.HML + RMWc + WML, data=factor.mat)
Inv = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(WML ~ FF.Rm + FF.SMB + FF.HML + RMWc + FF.CMA, data=factor.mat)
Mom = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

RMWc = cbind(Sh2, Mkt, Size, Val, Prof, Inv, Mom)
rownames(RMWc) = c("Mkt, SMB, HML, RMWc, CMA, WML")
res = rbind(res, RMWc)
# round(res, 3)
```

## Rm, SMB, HML, RMWg, CMA, WML

```{r}
factor.mat = f %>% select(FF.Rm, FF.SMB, FF.HML, RMWg, FF.CMA, WML)
factor.mat = factor.mat[1:630,]  # through 2015-12

R = matrix(colMeans(factor.mat), nrow=ncol(factor.mat), ncol=1)
covar.mat = cov(factor.mat)

# Max Sharpe Ratio
Sh2 = rbind(SR.sq.mat(R, covar.mat), sqrt(SR.sq.mat(R, covar.mat)[1]))[1]

# Marginal contributions from spanning regression

fit = lm(FF.Rm ~ FF.SMB + FF.HML + RMWg + FF.CMA + WML, data=factor.mat)
Mkt = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.SMB ~ FF.Rm + FF.HML + RMWg + FF.CMA + WML, data=factor.mat)
Size = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.HML ~ FF.Rm + FF.SMB + RMWg + FF.CMA + WML, data=factor.mat)
Val = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(RMWg ~ FF.Rm + FF.SMB + FF.HML + FF.CMA + WML, data=factor.mat)
Prof = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.CMA ~ FF.Rm + FF.SMB + FF.HML + RMWg + WML, data=factor.mat)
Inv = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(WML ~ FF.Rm + FF.SMB + FF.HML + RMWg + FF.CMA, data=factor.mat)
Inv = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

RMWg = cbind(Sh2, Mkt, Size, Val, Prof, Inv, Mom)
rownames(RMWg) = c("Mkt, SMB, HML, RMWg, CMA, WML")
res = rbind(res, RMWg)
# round(res, 3)
```

## Rm, SMB, HMLm, RMWor, CMA, WML

```{r}
factor.mat = f %>% select(FF.Rm, FF.SMB, HMLm, RMWor, FF.CMA, WML)
factor.mat = factor.mat[1:630,]  # through 2015-12

R = matrix(colMeans(factor.mat), nrow=ncol(factor.mat), ncol=1)
covar.mat = cov(factor.mat)

# Max Sharpe Ratio
Sh2 = rbind(SR.sq.mat(R, covar.mat), sqrt(SR.sq.mat(R, covar.mat)[1]))[1]

# Marginal contributions from spanning regression

fit = lm(FF.Rm ~ FF.SMB + HMLm + RMWor + FF.CMA + WML, data=factor.mat)
# round(coef(fit), 3)
# round(sd(fit$residuals), 3)
Mkt = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.SMB ~ FF.Rm + HMLm + RMWor + FF.CMA + WML, data=factor.mat)
# round(coef(fit), 3)
# round(sd(fit$residuals), 3)
Size = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(HMLm ~ FF.Rm + FF.SMB + RMWor + FF.CMA + WML, data=factor.mat)
# round(coef(fit), 3)
# round(sd(fit$residuals), 3)
Val = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(RMWor ~ FF.Rm + FF.SMB + HMLm + FF.CMA + WML, data=factor.mat)
# round(coef(fit), 3)
# round(sd(fit$residuals), 3)
Prof = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.CMA ~ FF.Rm + FF.SMB + HMLm + RMWor + WML, data=factor.mat)
# round(coef(fit), 3)
# round(sd(fit$residuals), 3)
Inv = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(WML ~ FF.Rm + FF.SMB + HMLm + RMWor + FF.CMA, data=factor.mat)
# round(coef(fit), 3)
# round(sd(fit$residuals), 3)
Mom = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

RMWor = cbind(Sh2, Mkt, Size, Val, Prof, Inv, Mom)
rownames(RMWor) = c("Mkt, SMB, HMLm, RMWor, CMA, WML")
res = rbind(res, RMWor)
# round(res, 3)
```

## Rm, SMB, HMLm, RMWc, CMA, WML

```{r}
factor.mat = f %>% select(FF.Rm, FF.SMB, HMLm, RMWc, FF.CMA, WML)
factor.mat = factor.mat[1:630,]  # through 2015-12

R = matrix(colMeans(factor.mat), nrow=ncol(factor.mat), ncol=1)
covar.mat = cov(factor.mat)

# Max Sharpe Ratio
Sh2 = rbind(SR.sq.mat(R, covar.mat), sqrt(SR.sq.mat(R, covar.mat)[1]))[1]

# Marginal contributions from spanning regression

fit = lm(FF.Rm ~ FF.SMB + HMLm + RMWc + FF.CMA + WML, data=factor.mat)
Mkt = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.SMB ~ FF.Rm + HMLm + RMWc + FF.CMA + WML, data=factor.mat)
Size = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(HMLm ~ FF.Rm + FF.SMB + RMWc + FF.CMA + WML, data=factor.mat)
Val = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(RMWc ~ FF.Rm + FF.SMB + HMLm + FF.CMA + WML, data=factor.mat)
Prof = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.CMA ~ FF.Rm + FF.SMB + HMLm + RMWc + WML, data=factor.mat)
Inv = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(WML ~ FF.Rm + FF.SMB + HMLm + RMWc + FF.CMA, data=factor.mat)
Mom = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

RMWc = cbind(Sh2, Mkt, Size, Val, Prof, Inv, Mom)
rownames(RMWc) = c("Mkt, SMB, HMLm, RMWc, CMA, WML")
res = rbind(res, RMWc)
# round(res, 3)
```

## Rm, SMB, HMLm, RMWg, CMA, WML

```{r}
factor.mat = f %>% select(FF.Rm, FF.SMB, HMLm, RMWg, FF.CMA, WML)
factor.mat = factor.mat[1:630,]  # through 2015-12

R = matrix(colMeans(factor.mat), nrow=ncol(factor.mat), ncol=1)
covar.mat = cov(factor.mat)

# Max Sharpe Ratio
Sh2 = rbind(SR.sq.mat(R, covar.mat), sqrt(SR.sq.mat(R, covar.mat)[1]))[1]

# Marginal contributions from spanning regression

fit = lm(FF.Rm ~ FF.SMB + HMLm + RMWg + FF.CMA + WML, data=factor.mat)
Mkt = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.SMB ~ FF.Rm + HMLm + RMWg + FF.CMA + WML, data=factor.mat)
Size = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(HMLm ~ FF.Rm + FF.SMB + RMWg + FF.CMA + WML, data=factor.mat)
Val = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(RMWg ~ FF.Rm + FF.SMB + HMLm + FF.CMA + WML, data=factor.mat)
Prof = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(FF.CMA ~ FF.Rm + FF.SMB + HMLm + RMWg + WML, data=factor.mat)
Inv = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

fit = lm(WML ~ FF.Rm + FF.SMB + HMLm + RMWg + FF.CMA, data=factor.mat)
Inv = (coef(fit)["(Intercept)"] / sd(fit$residuals))^2

RMWg = cbind(Sh2, Mkt, Size, Val, Prof, Inv, Mom)
rownames(RMWg) = c("Mkt, SMB, HMLm, RMWg, CMA, WML")
res = rbind(res, RMWg)
# round(res, 3) %>% as.data.frame
```

## Results

```{r}
round(res, 3) %>% as.data.frame
```


