% !TeX root=../main.tex

\subsection{Why Sharpe ratio? \textcite{barillas2016alpha}}

\textcite{pastor2000comparing}
\begin{quotation}
  A set of benchmarks that is correct for pricing need not be correct for 
  investing.
\end{quotation}


\textcite{jensen1968performance} explains that a regression intercept 
represents 
an asset's deviation from an asset pricing model.
$SMB$, $HML$, etc. are traded factors while Consumption growth is not.
\textcite{breeden2005intertemporal} suggests that non-traded factors can be 
replaced with mimicking traded ones.
Significant $\alpha$ means that the maximum Sharpe ratio of the factors used 
in the regression can be improved by a position in the asset being tested.

The asset pricing challenge is to describe a small number of observable 
factors that can come close to spanning an efficient portfolio. This is 
equivalent to correctly pricing returns.
Previous work tests factors' ability to price a small subset of returns, 
typically ``anomalies."
Tests should consider factors' ability to price \emph{all} returns.
In practice this means the stock returns available, including portfolio 
returns we can create with them, \emph{and} the factors themselves.

It is interesting to note when tests of subsets of asset returns do not point 
to the same combination of factors as tests involving a more complete set of 
returns.

\textcite{gibbons1989test} demonstrate that the possible improvement in the 
squared Sharpe ratio offered by test asset returns is given by the quadratic 
form in the $\alpha$s.
This measure of model misspecification shows that test assets are not 
important when comparing models.

Model $M_1$ composed of factors $f_1$ is preferable to model $M_2$ composed of 
factors $f_2$ if
\[
Sh^2(f_1, f_2, R) - Sh^2(f_1) < Sh^2(f_1, f_2, R) - Sh^2(f_2)
\]
Where $R$ represents test asset returns.
Since both sides measure the improvement in squared sharpe ratio when adding a 
factor to the set of test asset returns and additional factors,
we can simplify the condition to
\[
Sh^2(f_1, f_2) - Sh^2(f_1) < Sh^2(f_1, f_2) - Sh^2(f_2)
\]
\begin{quotation}
  Thus, the mis-pricing that matters for model comparison is the mis-pricing 
  of the factors in one model by the factors in the other model.
\end{quotation}

The condition can be simplified further to
\[
Sh^2(f_1)>Sh^2(f_2)
\]
Model comparison can be thought of in terms of investment opportunities.
Whether the model with the highest squared Sharpe ratio is ``good" enough 
depends on performance pricing test assets.

A model, $M$, is a multi-factor linear regression
\[
R = \alpha + \beta\cdot f + \varepsilon
\]
\textcite{gibbons1989test} show that
\[
\alpha ' \Omega^{-1}\alpha = Sh^2(f, R) - Sh^2(f)
\]
where $\Omega$ is the covariance matrix of $\varepsilon$.

\begin{quotation}
  The improvement in the squared Sharpe ratio equals the classic quadratic 
  form in the $\alpha$s of the additional returns
\end{quotation}

It may seem that trying to find the highest maximum Sharpe ratio means adding 
many factors.
Additional factors do not necessarily improve model performance.
For example, the three factor model of \textcite{fama1993common} explains the 
returns from sorts on size and accruals better than the five factor model 
outlined in \textcite{fama2015five}.
Consider two models; $R_i=\alpha+\beta_MR_M$ and 
$R_i=\alpha+\beta_MR_M+\beta_SSMB$ .
If a test asset's CAPM $\alpha$ is the opposite sign to its loading on $SMB$ 
then the $\alpha$ in the second model will be accentuated.
By conventional measures the second model is then "worse" than the first model.
The maximum Sharpe ratio of the second model is higher than the maximum Sharpe 
ratio for the first.
Conventional asset pricing tests and maximum sharpe ratios do not always agree.

If test asset and excluded-factor evidence contradict one another, we should 
favour excluded-factor evidence.
Excluded-factor evidence considers the returns on all assets rather than a 
subset of all assets.
Data mining is a problem for test assets (\textcite{lewellen2010skeptical}) 
and 
factors (\textcite{harvey2016and}).
