% !TeX root=../main.tex

\import{./Tables/}{Size_BMm_Prior_chars_tbl}
\import{./Tables/}{Size_BM_Inv_chars_tbl}

Value and momentum subsume investment and negate any contribution to
$\text{Sh}^2(\text{model 1})$.
This is shown by regressing investment on value, annual or monthly,
and momentum (not shown).
There is no intercept meaning there is no average unexplained return.
To explore why this is the case, I sort on value and momentum as well as
value and investment and interpret the variation in different
characteristics.
Table \ref{tbl:Size_BMm_Prior_chars} shows average value-weighted
characteristics for 32 size-$\text{BM}^m$-Prior portfolios and table
\ref{tbl:Size_BM_Inv_chars} shows average value-weighted characteristics for 32
size-BM-Inv portfolios.
The main message of the tables is that monthly value and momentum's
relationship with small, growth stocks' future change in BE is the opposite
that of annual value and investment.
Monthly value and momentum are a better proxy for changes in BE than investment.
For monthly value and momentum, small, growth stocks' future change in BE increases
from 0.31 to 0.61 as momentum buckets increase.
For annual value and investment, this relationship is reversed as small, growth stocks'
future change in BE decreases from 0.59 to 0.4 as investment buckets increase.
The variation in characteristics in table \ref{tbl:Size_BMm_Prior_chars} drive
many of the results for models \ref{eq:B16} and \ref{eq:F16} in subsets of portfolios.
A model has the potential to describe the returns on a given sort where the
characteristic used to construct factors are able to create variation in the
characteristic used to construct the subset of portfolios.
If increasing one characteristic increases another, this will drive
a positive and significant regression slope in time series regressions.
% Summary characteristics are not bound to regression slopes and a model will
% struggle where returns do not behave like the characteristics they are
% constructed from.
% These deviations are easy to identify because the change in
% regression slopes across buckets will not match the changes in the underlying
% characteristics across the same buckets. It is more difficult to identify
% \emph{why} returns do not follow the underlying characteristics.

Returns across $\text{BM}^m$ and Prior buckets range from 0.09 in the small,
low-$\text{BM}^m$ and low-Prior bucket to 2.04 in the small, high-$\text{BM}^m$
and high-Prior bucket.
Returns across BM and Inv buckets range from 1.01 in the big, low-BM and
low-Inv bucket to 1.46 in the small, high-BM and low-Inv bucket. 
The greater variation in returns for size-$\text{BM}^m$-Prior
portfolios is expected given the interaction between value and momentum.
Their interaction is also visible in the variation in returns at each
characteristic's extreme.
For example, in low-$\text{BM}^m$ the variation in returns across Prior buckets
is much larger, 0.09 to 1.47 for small stocks and 0.55 to 0.96 for big stocks,
than in high-$\text{BM}^m$ buckets, 1.01 to 2.04 for small stocks and 1.21 to
1.42 for big stocks.
The same is true of the variation in returns across $\text{BM}^m$ buckets in
the extreme Prior buckets.
Lower variation of returns across one characteristic in the extreme buckets of
the other mirrors findinings in \textcite{asness2013devil}.
Higher variation in returns for size, value and momentum sorts provides
potential to price more variation in returns than size, value and investment sorts.

% For both size-$\text{BM}^m$-Prior and size-BM-Inv portfolios, $\text{BM}^m$ is
% flat across Prior/Inv buckets and increases uniformly as $\text{BM}^m$/BM
% buckets increase. $\text{BM}^m$ is negatively related to Prior because strong
% recent returns will push ME up. This is not reflected in the Prior buckets
% because portfolios are rebalanced monthly.
For size-$\text{BM}^m$-Prior portfolios, BM increases as Prior buckets increase.
For example, in the high-$\text{BM}^m$ bucket, BM increases from 1.48 to 2.88
for small stocks and from 1.07 to 1.54 for big stocks.
Variation in BM within $\text{BM}^m$ buckets is undesirable because by sorting
on value we should keep value characteristics consistent within value buckets.
Consider a stock that is in the high-$\text{BM}^m$, high-Prior bucket in July,
just after annual BM is recalculated.
At this point in the year, $\text{BM}^m$ and BM are probably at their most
similar because ME values differ by six months compared to the maximum of eighteen.
If a stock has relatively high returns in the following months, high Prior,
its $\text{BM}^m$ will decrease as market equity increases while book equity
is held constant by a lack of new financial statements.
For a stock to remain in the high-$\text{BM}^m$, high-Prior bucket,
it must have had particularly high BM in order for high returns not to drag the
$\text{BM}^m$ down sufficiently to take the stock out of the
high-$\text{BM}^m$, high- Prior bucket.
% This effect is not seen in the size-BM-Inv sorts.

For the size-$\text{BM}^m$-Prior portfolios, Prior increases uniformly with Prior
buckets and is flat across $\text{BM}^m$ buckets.
The spread in Prior is larger for small stocks than big stocks.
In the small, growth bucket, Prior rises from -0.33 to 0.64.
In the big, growth bucket, Prior rises from -0.11 to 0.49.
For the size-BM-Inv portfolios, there is little variation in Prior across either
BM or Inv buckets.
Small stocks have higher average recent returns than big stocks with all small
stock values close to 0.2 while big stock values are close to 0.15.
The lack of variation in momentum characteristics means annual value and
investment will struggle to price the returns on momentum sorts.

Future variance is strongly related to size. Small stocks are more volatile
than big stocks with the average level and variation in variance
characteristics greater for small stocks.
Variance decreases marginally, from $\sim$0.2 to $\sim$0.1,
with momentum/investment buckets but only in small stocks.
For the most part, sorts on value and momentum/investment do not create
variation in the variance characteristic.
Monthly value and momentum as well as annual value and investment will struggle
to price the returns on subsets of portfolios constructed from sorts on variance.
The lack of variation in a characteristic designed to
capture volatility is counter-intuitive.
If anything, I would expect the variance characteristic to be too noisy,
rather than not noisy enough, to capture variation in the variance
characteristic.
This may reflect problems with my specification of variance.
I define variance as the variance of the prior month's daily returns.
I could have used a longer window and perhaps omitted the most recent month as
is common for constructing the momentum characteristic.

\textcite{fama2006profitability} use the dividend discount model to link the
profitability and investment factors to firm value.
With clean surplus accounting, the dividend discount model says that market
equity equals discounted expected future earnings less the future change in BE,
$ME_t = \sum_{s=1}^\infty E(Y_{t+s}-\Delta BE_{t+s})/R^s$
where $Y$ is earnings and $R$ is the gross discount rate.
Fama and French use change in assets in place of change in book equity.
I examine investment and change in BE characteristics to check if
investment is indeed a good proxy for changes in BE.

Future investment decreases across both $\text{BM}^m$ and Prior buckets for
both small and large stocks. In contrast to returns, the effects of each
characteristic are similar in the extreme buckets of the other. For example, in
the low-Prior bucket, Inv decreases from 0.39 to 0.2 for small stocks and
remains flat for big stocks. In the high-Prior bucket, Inv decreases from 0.25
to 0.06 for small stocks and from 0.22 to 0.09 for big stocks. In the
low-$\text{BM}^m$ bucket, Inv decreases from 0.39 to 0.25 for small stocks and
remains flat for big stocks. In the high-$\text{BM}^m$ bucket, Inv decreases
from 0.2 to 0.06 for small stocks and from 0.2 to 0.09 for big stocks. The
interaction of monthly value and momentum accounts for the variation in Inv in
small and big stocks. In size-BM-Inv sorts, Inv increases uniformly across Inv
buckets and remains flat across BM buckets.

In size-$\text{BM}^m$-Prior sorts, future change in BE in the low-$\text{BM}^m$
bucket increases from 0.31 to 0.61 as Prior increases.
In contrast, future change in BE in the low-BM bucket increases as Inv
decreases from 0.59 to 0.4 in size-BM-Inv sorts.
For both sorts, future change in BE moves in the opposite direction to the
Inv characteristic for small, growth stocks.
For size-$\text{BM}^m$-Prior sorts, Inv increases while future change in BE
decreases while for size-BM-Inv sorts, Inv decreases while future change in
BE increases.
Investment is not an appropriate proxy for changes in BE.
Furthermore, value and momentum capture variation in investment and changes in BE.

% Value and momentum enhance each other's slopes in time series regressions.
% Any two variables that are negatively correlated with each other but positively
% correlated with the independent variable will exhibit this effect
% \parencite{fama2015incremental}.
% Sorts on value and momentum to show their strength is not just
% statistical but also economic through their ability to forecast changes in BE.
% Using the dividend discount model logic of Fama and French,
% Inv is used as a proxy for changes in BE.
% This divergence of logic and data suggests asset growth, Inv,
% is not the best proxy for changes in BE.
