% !TeX root=../main.tex

Table \ref{tbl:replicated_factors} shows summary statistics for selected \emph{replicated}
factors. The factors shown demonstrate annual and monthly rebalancing portfolios for those
factors not available online, $PMU^{16}$ and $PMU$, and  or for variables that I use to
produce my own sorts; $HML$, $HML^m$, $CMA$ and $WML$. I include $PMU^{06}$ to give some
credibility to the cash profitability factor not available online. The main message of the
table is that my results are not total garbage. Values should be compared to Dr. Kenneth
French's website for all factors except $HML^m$ which should be compared to data available
from AQR Captial Management. All factors are significant, the t-statistics are above 2,
and highly correlated with their ``true" online counter-parts. The minimum correlation is
0.96 for $CMA$.

The largest replication problems are caused by the investment factor, $CMA$, with an
average return of 0.22\% per month. The average return is 7 basis points, b.p., below the
factor available from Dr. Ken. The replicated annual value factor, $HML$, is 4 b.p. below
Dr. Ken's factor. The replicated profitibility factor including R\&D costs and accruals,
$PMU^{06}$ is 3 b.p. above Dr. Ken's factor. The replicated momentum factor, $WML$, is 8
b.p. below Dr. Ken's factor. The replicated monthly value factor, $HML^m$, is 5 b.p. above
the factor available from AQR. It is worth noting that AQR use book-price rather than
book-to-market as their second sort variable. The intuition of capturing the value
premium is the same.
